---
title: "wonderland version of unreal code"
output: html_notebook

---

```{r setup}
knitr::opts_knit$set(root.dir = normalizePath("."))
options('stringsAsFactors'=FALSE)
```

updating Ureal code to work with wonderland's parameters 
i decided not to mess with rdas, so all code will be directly in the script .

loading all libraries
```{r warning=FALSE}
# loading all libraries
 library(stringi)
 library(data.table)
 library(ggplot2) #ploting tool
 library(tidyr) #data wrangling tool
 library(cowplot) #for arranging plots together
 library(stringi)#for manipulating strings
 library(dplyr) #dplyr is a grammar of data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges
 library(tidyverse) #R packages designed for data science

 # study_number<-4 // dont know what this is 

```
names od domains and conditions used

creating paths
```{r}

  sub_number <- readline(prompt="Enter subject number: ")
  study_number <- 4
  # subject folder must be in the parent folder of r function
   subject_folder<-paste(dirname(getwd()),'/Subject_data_unreal_04/sub_',sub_number, sep = "")  
  
  # 'rating folder' is grandfather folder from code
  ratings_folder<-dirname(dirname(subject_folder))
  results_folder<-paste(subject_folder, '/results_sub_',  sub_number , sep ="")
  
  # creating easily accessible paths
  rda_folder<-paste(ratings_folder, '/rdas', sep="")

  #paths[1] is the subject folder
  #paths[2] is the ratings folder
  #paths[3] is the results folder
  #paths[4] is the rdas folder
  
  paths<-c(subject_folder,ratings_folder,results_folder,rda_folder)
  
```

loading CSV's this section is senstive to orgnzation, if data saving changes this will need modifcation
```{r warning=FALSE}
# loading CSV's this section is senstive to orgnzation, if data saving changes this will need modifcation
  setwd(paths[1])
  
  
  # results_sub_xxx

  trials  <- read.exe(dir()[2],header=FALSE, stringsAsFactors = FALSE)
  reality_rating <- read.exe(dir()[1],header=TRUE, stringsAsFactors = FALSE)
  
  # adding sub name
  reality_rating <- reality_rating %>% mutate(Subject = sub_number)
  trials <- trials %>% mutate(Subject = sub_number)

  setwd(paths[2])
  
```

data check - see if input is correct
```{r}
#hard codded number of trials 07/12/22
correct_number_of_rows<-150

#check how many rows there are in the ratings file
number_of_rows<-nrow(reality_rating)
if (nrow(reality_rating)==correct_number_of_rows){
  cat("Number of trials is correct","\n")
}else if (number_of_rows>correct_number_of_rows) {
  extra_rows<-number_of_rows-correct_number_of_rows
  cat(paste("There are", as.character(extra_rows), "more rows than usuall"),"\n")
  reality_rating<-reality_rating[1:correct_number_of_rows,]
  cat(paste("There should be",as.character(number_of_rows),"rows"),"\n")
  cat("The extra rows were removed","\n")
} else if (number_of_rows < correct_number_of_rows){
  missing_rows<-correct_number_of_rows-number_of_rows
  cat(paste("There are", as.character(missing_rows),"missing rows in this file"))
}

```
filter data that is not a trial
```{r}
# removing id's of non trail codes
reality_rating<- reality_rating %>% filter (BlockNumber!=777 & BlockNumber!=666 & BlockNumber!=9999 & BlockNumber!=9992 & BlockNumber!=80)

# taking filtered questions
filter_questions <-reality_rating$QuestionID==1
reality_rating<-reality_rating[filter_questions,]

#removing unused columns
reality_rating<-subset(reality_rating, select=-c(TimesatmpInitialDirection,InitialDirection,ProbabilityComment,SessionID,Phase,QuestionID,TimeStampStartQuestion,TimestampEndQuestion,ResponseTime,TimeOfVaseHit,NegativeAnswersCount,PositiveAnswersCount,ConvertedValue,StairCaseValue,ConsequtiveCounter ))
colnames(reality_rating)[4]<-"RealityRating"
colnames(reality_rating)[3]<-"ConditionCode"
colnames(reality_rating)[2]<-"Level"
colnames(reality_rating)[1]<-"TrialNumber"

reality_rating <- reality_rating %>% mutate(StimVal = RealityRating)
#save on original just in case
reality_rating <- reality_rating %>% mutate(org_StimVal = StimVal)
```

create the names of the conditions and domains of reality_rating
```{r}
# creates 2 new columns that are named condtionname and domain

  reality_rating$ConditionName[reality_rating$ConditionCode==29]<-"Delay"
  reality_rating$ConditionName[reality_rating$ConditionCode==221]<-"Low Gravity"
  reality_rating$ConditionName[reality_rating$ConditionCode==222]<-"High Gravity"
  reality_rating$ConditionName[reality_rating$ConditionCode==33]<-"Ripple"
  reality_rating$ConditionName[reality_rating$ConditionCode==301]<-"Low Saturation"
  reality_rating$ConditionName[reality_rating$ConditionCode==302]<-"High Saturation"
  reality_rating$ConditionName[reality_rating$ConditionCode==601]<-"Shrink"
  reality_rating$ConditionName[reality_rating$ConditionCode==602]<-"Grow"
  reality_rating$ConditionName[reality_rating$ConditionCode==121]<-"Slow Time"
  reality_rating$ConditionName[reality_rating$ConditionCode==122]<-"Fast Time"
  
  reality_rating$Domain[reality_rating$ConditionCode==29]<-"Self"
  reality_rating$Domain[reality_rating$ConditionCode==221]<-"Nature"
  reality_rating$Domain[reality_rating$ConditionCode==222]<-"Nature"
  reality_rating$Domain[reality_rating$ConditionCode==33]<-"Perception"
  reality_rating$Domain[reality_rating$ConditionCode==301]<-"Perception"
  reality_rating$Domain[reality_rating$ConditionCode==302]<-"Perception"
  reality_rating$Domain[reality_rating$ConditionCode==601]<-"Self"
  reality_rating$Domain[reality_rating$ConditionCode==602]<-"Self"
  reality_rating$Domain[reality_rating$ConditionCode==122]<-"Nature"
  reality_rating$Domain[reality_rating$ConditionCode==121]<-"Nature"
```

i have no idea why this was done
```{r}
#reality_rating<-reality_rating %>% group_by(ConditionName) %>% mutate(Domain = ConditionCode)

#reality_rating<-reality_rating %>% group_by(ConditionCode) %>% mutate(ConditionName = ConditionCode)

```

give ratings to diffrent outcomes per trial, save original data

for some reason may only work if ran line by line
```{r warning=FALSE}

reality_rating<-reality_rating %>% mutate (TrialType = ConditionName)
reality_rating$TrialType <- as.character(reality_rating$TrialType) 
reality_rating$TrialType[reality_rating$TrialType!="Baseline"] <- "Trial"

# something weird happens here with coerced NA's
reality_rating$Level<-as.numeric(reality_rating$Level)
reality_rating$ConditionName[reality_rating$Level==0]<-"Baseline"
# remove rows where the subject did not answer in time
no_ans_filter <- reality_rating$RealityRating != "NoAnswerInTime"
reality_rating <- reality_rating[no_ans_filter,]

# some variable editing
reality_rating$RealityRating<-as.numeric(reality_rating$RealityRating)
reality_rating$Level<-as.factor(reality_rating$Level)

# Adding condition names
reality_rating$ConditionName<-factor(reality_rating$ConditionName, levels=c("Grow","Shrink","Delay","Slow Time","Fast Time","Low Gravity","High Gravity","Ripple","Low Saturation","High Saturation","Baseline"))

# Adding domain names
reality_rating$Domain<-factor(reality_rating$Domain, levels=c("Self","Nature","Perception"))

# Make sure you have a baseline filter df
baseline_filter<-drop_na(reality_rating %>% filter(TrialType %in% c("Baseline")),any_of("RealityRating"))

average_baseline_rating<-round(mean(baseline_filter$RealityRating),2)
cat("\n","Average baseline ratings was:",average_baseline_rating,"\n")
cat("SD of baseline ratings was:",round(sd(baseline_filter$RealityRating),2),"\n")


# save original df with unrandomized baseline trials
original_ratings<-reality_rating

# original code had this blocjed off so leaving it in case later there is a reason to add

#(paths[3])
#filename<-gsub(" ","",paste("reality_ratings_",sub_number,".csv"))
#fwrite(original_ratings,paste("original_order_",filename),col.names=TRUE)


# check baseline trials after randomized sampling
org_baseline_filter<-drop_na(original_ratings %>% filter(TrialType %in% c("Baseline")),any_of("RealityRating"))


##add column without out layers  

# add adapted_scales column for looking at raw units
reality_rating<-reality_rating %>% mutate(adapted_scales = StimVal)

# make sure you have a baseline filter df
baseline_filter<-drop_na(reality_rating %>% filter(ConditionName %in% c("Baseline")),any_of("RealityRating"))

```

arrange trails by what was displayed to the subject
```{r}
colnames(trials)<-c("Magnitude","ConditionCode","C","D","E","Height","G","H","I","J","K","Time","M","N","O","P","Q","R","S","T","U","Gravity","Duration","Blackscreen","SlideCode","Show","Codes","AB","Delay","Saturation","AE","AF","Ripple","AH","AI","AJ","sub_num")

trials<-subset(trials, select=-c(C,D,E,G,H,I,J,K,M,N,O,P,Q,R,S,T,U,Duration,Blackscreen,SlideCode,Show,Codes,AB,AE,AF,AH,AI,AJ))

#round the numbers becasue the zeros are distracting
trials[,3:8]<-round(trials[,3:8],5)

#cleaning out non-stimuli rows
trials<- trials %>% filter (ConditionCode!=777 & ConditionCode!=666 & ConditionCode!=9999 & ConditionCode!=9992 & ConditionCode!=80 & ConditionCode!=11 & ConditionCode!=22 & ConditionCode!=333 & ConditionCode!=44 & ConditionCode!=55)

#naming conditions and domains
trials<-trials %>% group_by(ConditionCode) %>% mutate(ConditionName = ConditionCode)
trials<-trials %>% group_by(ConditionName) %>% mutate(Domain = ConditionCode)
```



create the names of the conditions and domains of trails
```{r}
# creates 2 new columns that are named condtionname and domain

  trials$ConditionName[trials$ConditionCode==29]<-"Delay"
  trials$ConditionName[trials$ConditionCode==221]<-"Low Gravity"
  trials$ConditionName[trials$ConditionCode==222]<-"High Gravity"
  trials$ConditionName[trials$ConditionCode==33]<-"Ripple"
  trials$ConditionName[trials$ConditionCode==301]<-"Low Saturation"
  trials$ConditionName[trials$ConditionCode==302]<-"High Saturation"
  trials$ConditionName[trials$ConditionCode==601]<-"Shrink"
  trials$ConditionName[trials$ConditionCode==602]<-"Grow"
  trials$ConditionName[trials$ConditionCode==121]<-"Slow Time"
  trials$ConditionName[trials$ConditionCode==122]<-"Fast Time"
  
  trials$Domain[trials$ConditionCode==29]<-"Self"
  trials$Domain[trials$ConditionCode==221]<-"Nature"
  trials$Domain[trials$ConditionCode==222]<-"Nature"
  trials$Domain[trials$ConditionCode==33]<-"Perception"
  trials$Domain[trials$ConditionCode==301]<-"Perception"
  trials$Domain[trials$ConditionCode==302]<-"Perception"
  trials$Domain[trials$ConditionCode==601]<-"Self"
  trials$Domain[trials$ConditionCode==602]<-"Self"
  trials$Domain[trials$ConditionCode==122]<-"Nature"
  trials$Domain[trials$ConditionCode==121]<-"Nature"
```

Creating a 'stimulation Value' column which will represent all the values presented to the subject, in one vector

```{r}

#baseline presentations are defined as 'zero' value for all conditions, so I am going to zero all the values in the trials df that are not a specific condition level
#change baseline Time value to zero
trials$Time[trials$Time==1]<-0
#change baseline Gravity to zero
trials$Gravity[trials$Gravity==-9.81]<-0
#make a stim_val column
trials$StimVal = rowSums(trials[,c("Height","Time","Gravity","Delay","Saturation","Ripple")])

trials$Time[trials$Time==0]<-1
#change baseline Gravity to zero
trials$Gravity[trials$Gravity==0]<-(-9.81)

if (any(reality_rating$BlockNumber!=trials$ConditionCode)){
 cat("### WARNING: There are mismatched trial rows in the file! ###","\n")
}

```


create a folder for results, if running the script , times from this point on, than you must erase the folder "results_sub_m".
```{r warning=FALSE}
# create a folder for results based on path that was created
  try(dir.create(paths[3]))
```

we have to make sure the baseline values for gravity/time are not zero
```{r}

low_gravity_rows<-which(reality_rating$original_condition_names == "Low Gravity" & reality_rating$StimVal == 0)

if (length(low_gravity_rows) != 0){reality_rating$StimVal[low_gravity_rows]<-(-9.81)}


#add a filename column
reality_rating<-reality_rating %>% mutate(Filename = dir()[2])

#add a pilot number column
reality_rating<-reality_rating %>% mutate(Study  = study_number)

#add an outlier detection column
reality_rating<-reality_rating %>% mutate(Outlier = 0)


```

for wonderland removing unneeded iterations taking only needed, if changed at any point change here
```{r}

ConditionName_vec <- c("Low Gravity","Delay","Ripple", "Baseline")

# plot list
plot_list<-vector(mode = "list", length=length(ConditionName_vec))
```

find average rating per condition
```{r}
#loop over each condition in Condition Name
for (i in ConditionName_vec){
  
  condition_indices<-which(reality_rating$ConditionName==i)
  condition_df<-reality_rating[condition_indices,]
  
  for (y in unique(as.numeric(condition_df$Level))){
    #find indices of a level within the entire df
    condition_and_level_indices<-which(reality_rating$ConditionName==i & reality_rating$Level==y)
    
    #find outliers, set at 2STD
    average_rating<-mean(reality_rating$RealityRating[condition_and_level_indices])
    sd_ratings<-2*sd(reality_rating$RealityRating[condition_and_level_indices])
   
     #calculate the upper and lower limits for each set
    low_lim<-average_rating-sd_ratings
    high_lim<-average_rating+sd_ratings
    
    #find indices of the outlier values, change the value of outliar to 1
    for (n in condition_and_level_indices){
      if(!between(reality_rating$RealityRating[n],low_lim,high_lim)){
        reality_rating[n,"Outlier"]<-1
      }
    }
  }
}

#create a data frame with outliers filtered out
reality_rating_no_outliers<- reality_rating %>% filter (Outlier!=1)
```

normalizing and saving data frame. one  csv is saved here in folder
```{r warning=FALSE}
# max and min non-outlier ratings
reality_rating<- reality_rating %>% mutate (avg_norm = RealityRating)
max_rating<-max(reality_rating$RealityRating)
min_rating<-min(reality_rating$RealityRating)
mean_rating<-mean(reality_rating$RealityRating)

# normalizing rating as a fraction of 1 n/max(n)
reality_rating$avg_norm<-(reality_rating$RealityRating-mean_rating)/(max_rating-min_rating)

# creating z_scores
reality_rating<- reality_rating %>% mutate (z_score = RealityRating)
sd_rating<-sd(reality_rating$RealityRating)
reality_rating$z_score<-(reality_rating$RealityRating-mean_rating)/sd_rating

#rounding some columns
reality_rating$avg_norm<-round(reality_rating$avg_norm,digits = 4)
reality_rating$z_score<-round(reality_rating$z_score,digits = 4)
```

```{r}
# add exclusion criteria 
exlusion_criteria = 0

# when turning catgory into integer the system adds 1 so it starts from 1 and not 0
base_lv = min(as.integer(reality_rating$Level)) - 1

max_lv = max(as.integer(reality_rating$Level)) -1

# looking for base line mean and highest alteration mean
base_line_ratings = mean(reality_rating$RealityRating[reality_rating$Level == base_lv])
highest_lv_ratings = mean(reality_rating$RealityRating[reality_rating$Level == max_lv])

# counting how many conditions got through
numof_condions = table(reality_rating$ConditionName)
exlude_condition = numof_condions >= 4
exlude_condition = names(exlude_condition[exlude_condition == TRUE])
exlude_condition = paste ("met criteria of 4 instences:", toString(paste(exlude_condition)))

# creating exclusion veriable

if ((base_line_ratings - highest_lv_ratings < 10)||(base_line_ratings < 60)){
  exlusion_criteria = 1
}
```


```{r warning=FALSE}
#save the new data frames you created
setwd(paths[3])
if (exlusion_criteria == 0){
  filename<-gsub(" ","",paste("reality_ratings_",sub_number,".csv"))
} else {
  filename<-gsub(" ","",paste("exluded reality_ratings_",sub_number,".csv"))
}

fwrite(reality_rating,filename,col.names=TRUE)
```


plotting with outliyers
Basic plot of ratings without normalization
```{r warning=FALSE}
# change stimval into a integer for calculations

setwd(paths[3])

reality_rating$StimVal = as.integer(reality_rating$StimVal)

for (x in 1:length(ConditionName_vec)){
  # filter out the rows of the current condition
  current_cond<-reality_rating[reality_rating$ConditionName==ConditionName_vec[x],]
  
  # trials filtered by domain
  current_domain<-current_cond$Domain[1]
  
  # domain by specific condition
  current_base_stimval<-reality_rating[reality_rating$ConditionName == ConditionName_vec[x],]
  
  # baseline will be lowest lv
  current_base_stimval<-current_base_stimval[current_base_stimval$Level==1,]
  
  # baseline of stimulus will be average stimulation per group
  current_base_stimval<-mean(current_base_stimval$StimVal)
  
  # all plots start at base line
  current_baseline_filter<-baseline_filter
  current_baseline_filter$StimVal<-current_base_stimval
  current_baseline_filter$Domain<-current_domain
  
  # making a plot, no need for some colomn
  current_cond<-rbind(current_cond[,1:11],current_baseline_filter)

  #plot by level of alteration and add to plot list
  plot_list[[x]]<- ggplot(current_cond, aes(x=Level, y=RealityRating,fill=Domain)) +
    geom_boxplot(position="dodge",color="black",outlier.shape = NA)+guides(fill=FALSE)+
    scale_fill_manual(values = c("Nature" = "springgreen3","Perception"="slateblue3","Self"="indianred2"))+
    scale_color_manual(values=c("#00ff00")) + 
    geom_jitter(color="black", width=0.15, alpha=0.95) +
    geom_smooth(formula= y~x,method = "loess", se=TRUE, level=0.95, alpha=.55,aes(group=1),color="navy") +
    ylab("Rating")+
    ylim(0,100)+
    ############################# change lv in wonderland_02 ##################
    
    scale_x_discrete(labels = c('Base','1','2','3','4')) +
    theme_classic(base_size= 12)+
    theme(axis.text=element_text(face="bold",color="black",size=6),axis.title=element_text(face="bold",color="black",size=7,vjust=-1),plot.title =element_text(face="bold",color="black",size=9,hjust=0.5,vjust=-1) )+
    ggtitle(ConditionName_vec[x])
}

#saving the grid
if (exlusion_criteria == 0){
  png_title<-paste("Sub",as.character(sub_number), "Average Ratings.png")
} else {
  png_title<-paste("Sub",as.character(sub_number), "exluded Average Ratings.png")
}

final_plot<-cowplot::plot_grid(plotlist = plot_list,nrow=1,ncol=4, rel_heights = c(1,1),greedy=TRUE)
#show the plot
final_plot+draw_figure_label(paste("Sub",as.character(sub_number),"average", exlude_condition),position = "bottom.left" ,size=8,fontface = "bold")
#save the plot
ggsave(png_title,scale=1,width=29,height=15,units="cm",dpi=600)


```

Ratings with Raw Unity Values
```{r  warning=FALSE}
setwd(paths[3])

for (x in 1:length(ConditionName_vec)){
  #filter out the rows of the current condition
  current_cond<-reality_rating[reality_rating$ConditionName==ConditionName_vec[x],]
  
  # trials filtered by domain
  current_domain<-current_cond$Domain[1]
  
  # trial domain by specific condition 
  current_base_stimval<-reality_rating[reality_rating$ConditionName==ConditionName_vec[x],]
  
  # baseline will be lowest lv
  current_base_stimval<-current_base_stimval[current_base_stimval$Level==1,]
  
  # baseline of stimulus will be average stimulation per group
  current_base_stimval<-mean(current_base_stimval$StimVal)
  
  # all plots start at base line
  current_baseline_filter<-baseline_filter
  current_baseline_filter$StimVal<-current_base_stimval
  current_baseline_filter$Domain<-current_domain
  
  # making a plot, no need for some colomn
  current_cond<-rbind(current_cond[,1:11],current_baseline_filter)
  
  #we are currently not removing outliers, under the assumption that all ratings are valid judgments (13.7.22 Gadi)
  
  
  #current_cond<-remove_outliers(current_cond)
  #plot by level of alteration and add to plot list
  plot_list[[x]]<-ggplot(current_cond, aes(x=as.factor(StimVal), y=RealityRating,fill=Domain)) +
    geom_boxplot(position="dodge",color="black",outlier.shape = NA)+guides(fill=FALSE)+
    scale_fill_manual(values = c("Nature" = "springgreen3","Perception"="slateblue3","Self"="indianred2"))+
    scale_color_manual(values=c("#00ff00")) + 
    geom_jitter(width=.15,alpha=.95)+
    geom_smooth(formula= y~x,method = "loess", se=TRUE, level=0.95, alpha=.55,aes(group=1),color="navy") +
    ylab("Rating")+
    ylim(0,100)+
    xlab("Unity")+
    theme_classic(base_size= 12)+
    theme(axis.text=element_text(face="bold",color="black",size=6),axis.title=element_text(face="bold",color="black",size=7,vjust=-1),plot.title =element_text(face="bold",color="black",size=11,hjust=0.5,vjust=-1) )+
    ggtitle(current_cond$ConditionName[1])
 
  # reverse so that it reads left to right
  plot_list[[x]]<-plot_list[[x]]+scale_x_discrete(limits=rev)
}



if (exlusion_criteria == 0){
  png_title<-paste("Sub",as.character(sub_number), " Ratings ~ Raw.png")
} else{
  png_title<-paste("Sub",as.character(sub_number), "exluded Ratings ~ Raw.png")
}
final_plot_3<-cowplot::plot_grid(plotlist = plot_list,nrow=1,ncol=3,rel_heights = c(1,1),greedy=TRUE)
#show the plot
final_plot_3+draw_figure_label(paste("Sub",as.character(sub_number)," Ratings ~ Raw", exlude_condition),position = "bottom.left" ,size=8,fontface = "bold")
#save the plot
ggsave(png_title,scale=1,width=29,height=8,units="cm",dpi=600)

```

plotting without outliyers
Basic plot of ratings without normalization

```{r  warning=FALSE}

setwd(paths[3])
for (x in 1:length(ConditionName_vec)){
  #filter out the rows of the current condition
  current_cond<-reality_rating_no_outliers[reality_rating_no_outliers$ConditionName==ConditionName_vec[x],]
  
  # trials filtered by domain
  current_domain<-current_cond$Domain[1]
  
  # trial domain by specific condition 
  current_base_stimval<-reality_rating_no_outliers[reality_rating_no_outliers$original_condition_names==ConditionName_vec[x],]
  
  # baseline will be lowest lv
  current_base_stimval<-current_base_stimval[current_base_stimval$Level==1,]
  
  # baseline of stimulus will be average stimulation per group
  current_base_stimval<-mean(current_base_stimval$StimVal)
  
  # all plots start at base line
  current_baseline_filter<-baseline_filter
  current_baseline_filter$StimVal<-current_base_stimval
  current_baseline_filter$Domain<-current_domain
  
  # making a plot, no need for some colomn
  current_cond<-rbind(current_cond[,1:11],current_baseline_filter)
  
  #not removing outliers
  #current_cond<-remove_outliers(current_cond)
  #plot by level of alteration and add to plot list
  plot_list[[x]]<- ggplot(current_cond, aes(x=Level, y=RealityRating,fill=Domain)) +
    geom_boxplot(position="dodge",color="black",outlier.shape = NA)+guides(fill=FALSE)+
    scale_fill_manual(values = c("Nature" = "springgreen3","Perception"="slateblue3","Self"="indianred2"))+
    scale_color_manual(values=c("#00ff00")) + 
    geom_jitter(color="black", width=0.15, alpha=0.95) +
    geom_smooth(formula= y~x,method = "loess", se=TRUE, level=0.95, alpha=.55,aes(group=1),color="navy") +
    ylab("Rating")+
    ylim(0,100)+
    scale_x_discrete(labels = c('Base','1','2','3','4')) +
    theme_classic(base_size= 12)+
    theme(axis.text=element_text(face="bold",color="black",size=6),axis.title=element_text(face="bold",color="black",size=7,vjust=-1),plot.title =element_text(face="bold",color="black",size=9,hjust=0.5,vjust=-1) )+
    ggtitle(current_cond$ConditionName[1])
}

#saving the grid
if(exlusion_criteria == 0){
  png_title<-paste("Sub",as.character(sub_number), "Average Ratings no outliers.png")
} else  {
  png_title<-paste("Sub",as.character(sub_number), "exluded Average Ratings no outliers.png")
}

final_plot<-cowplot::plot_grid(plotlist = plot_list,nrow=1,ncol=3,rel_heights = c(1,1),greedy=TRUE)
#show the plot
final_plot+draw_figure_label(paste("Sub",as.character(sub_number),"average", exlude_condition),position = "bottom.left" ,size=8,fontface = "bold")
#save the plot
ggsave(png_title,scale=1,width=29,height=15,units="cm",dpi=600)
```

Ratings with Raw Unity Values, without outliers
```{r  warning=FALSE}
setwd(paths[3])
for (x in 1:length(ConditionName_vec)){
  #filter out the rows of the current condition
  current_cond<-reality_rating_no_outliers[reality_rating_no_outliers$ConditionName==ConditionName_vec[x],]
  
  # trials filtered by domain
  current_domain<-current_cond$Domain[1]
  
  # trial domain by specific condition 
  current_base_stimval<-reality_rating_no_outliers[reality_rating_no_outliers$original_condition_names==ConditionName_vec[x],]
  
  # baseline will be lowest lv
  current_base_stimval<-current_base_stimval[current_base_stimval$Level==1,]
  
  # baseline will be lowest lv
  current_base_stimval<-mean(current_base_stimval$StimVal)
  
  # baseline of stimulus will be average stimulation per group
  current_baseline_filter<-baseline_filter
  current_baseline_filter$StimVal<-current_base_stimval
  current_baseline_filter$Domain<-current_domain
  
  # making a plot, no need for some colomn
  current_cond<-rbind(current_cond[,1:11],current_baseline_filter)
  
  #we are currently not removing outliers, under the assumption that all ratings are valid judgments (13.7.22 Gadi)
  #plot by level of alteration and add to plot list
  plot_list[[x]]<-ggplot(current_cond, aes(x=as.factor(StimVal), y=RealityRating,fill=Domain)) +
    geom_boxplot(position="dodge",color="black",outlier.shape = NA)+guides(fill=FALSE)+
    scale_fill_manual(values = c("Nature" = "springgreen3","Perception"="slateblue3","Self"="indianred2"))+
    scale_color_manual(values=c("#00ff00")) + 
    geom_jitter(width=.15,alpha=.95)+
    geom_smooth(formula= y~x,method = "loess", se=TRUE, level=0.95, alpha=.55,aes(group=1),color="navy") +
    ylab("Rating")+
    ylim(0,100)+
    xlab("Unity")+
    theme_classic(base_size= 12)+
    theme(axis.text=element_text(face="bold",color="black",size=6),axis.title=element_text(face="bold",color="black",size=7,vjust=-1),plot.title =element_text(face="bold",color="black",size=11,hjust=0.5,vjust=-1) )+
    ggtitle(current_cond$ConditionName[1])
  
  # reverse so that it reads left to right
  plot_list[[x]]<-plot_list[[x]]+scale_x_discrete(limits=rev)
}


#saving the grid
if (exlusion_criteria == 0){
  png_title<-paste("Sub",as.character(sub_number), " Ratings raw unity no outliers.png")
} else{
  png_title<-paste("Sub",as.character(sub_number), " exluded Ratings raw unity no outliers.png")
}

final_plot_3<-cowplot::plot_grid(plotlist = plot_list,nrow=1,ncol=4,rel_heights = c(1,1),greedy=TRUE)
#show the plot
final_plot_3+draw_figure_label(paste("Sub",as.character(sub_number)," Ratings ~ Raw",exlude_condition),position = "bottom.left" ,size=8,fontface = "bold")
#save the plot
ggsave(png_title,scale=1,width=29,height=8,units="cm",dpi=600)
```



